---
title: "Notes of data_wrangling_tidyverse"
output:
  word_document: default
  pdf_document: default
---

# Data Wrangling Process
Data from https://www.kaggle.com/c/house-prices-advanced-regression-techniques

Data was already split into test and train data sets.
- Train data set contained 1,460 rows and 81 columns
- Test data set contained 1,459 rows and 80 columns (minus the SalePrice column, which will be predicted)

## Step 1: The test and train data sets were combined for pre-processing. How?
- A new column named 'label_split' was added to both data sets to facilitate later re-split. The value 'train' was added to the 'label_split' for train data set and the value 'test' for the test data set.
- The column 'SalePrice' was added to the test data set and the value NA was assigned to all rows.
- A merged data set was created using rbind() and contained 2,919 rows and 82 columns.

## Step 2: 
- The merged data set (train and test) has 80 features, with 6% of missing data.

```{r setup, include = FALSE}
library(naniar)
View(features_df)
```

```{r, echo=FALSE}
vis_miss(features_df, cluster=TRUE)
```

- Dropping columns:
- The column 'Alley' measures the type of alley access to property in three levels (Grvl = Gravel, Pave	= Paved, NA = No alley access). NA is not in fact missing data but data stating that houses have no alley. The NA values were then replaced by 'NoAlley'.
- The column 'PoolQC' measures the pool quality in five levels(Ex =Excellent, Gd = Good, TA = Average/Typical, Fa = Fair, NA = No Pool). NA is not in fact missing data but data stating that houses have no pool. The NA values were then replaced by 'NoPool'.
- 'Fence' -> NA equals NoFence
- 'MiscFeature' -> NA equals NoMisc

- For MasVnrType (Masonry veneer type) and MasVnrArea (Masonry veneer area in square feet), the NA values correspond to the same rows and are not a reference to no masonry veneer. it looks like it's a true missing value. Deal with it by imputation? Method?

- MSZoning - 4 NAs were replaced based on the most frequent MSZoning for each type of MSSubClass. This replacement shouldn't impact analysis, but no tests were made to confirm that.



Dealing with date variables --> Lubridate
Date variables = YearBuilt, YearRemodAdd, GarageYrBlt, MoSold, YrSold
MoSold: Month Sold (MM)
YrSold: Year Sold (YYYY)

